### 2013-12-03 manuscripts/reply/reply-si-main.tex
Working on reply ms.
Adding reference for dpp-msbayes manuscript to `references.bib`, moving
sections from `short-reply.tex` to `reply-si-main.tex`, and miscallenous
edits throughout `short-reply.tex`.

>>>>

\section*{Other clarifications}

\subsection*{Graphical prior comparisons}
\citet{Hickerson2013} advocate the use of what they call graphical checks of
prior models.
This entails generating a small number (1000) of random samples from the prior
and plotting the resulting summary statistics in comparison to the observed
statistics to see if they coincide (see Figure 1 of \citet{Hickerson2013}).
As we show above, this strategy can be misleading, because the resulting plots
of this approach have little correlation with the appropriateness of priors.
Given the richness of the \msb model ($\approx 600$ parameters for the Philippine
dataset analyzed by \citet{Hickerson2013}), we do not expect that 1000
\emph{random} draws from the vast prior parameter space will yield data and
summary statistics consistent with the observed data.
In fact, when such random draws are tightly clustered around the observed
statistics, this can be an indication that the prior is over-fit, as we show
above (Table~\ref{tabModelChoiceEmpirical} and Figure~\ref{figPCA}).
Thus, using such plots to select priors should be avoided, and the use of
posterior predictive analyses would be much more informative about the overall
fit of models.

\subsection*{Saturation of summary statistics}
\citet{Hickerson2013} claim the priors used by \citet{Oaks2012} ``cause much of
the explored parameter space to be beyond the threshold of saturation in most
mtDNA genes.'' To explore this possibility, we simulated datasets under prior
settings that match two of the three priors used by \citet{Oaks2012}:
$\meanDescendantTheta{} \sim U(0.0005, 0.04)$ and $\ancestralTheta{} \sim
U(0.0005, 0.02)$.
Under this prior, we draw divergence time parameters from a uniform
distribution of $U(0, 20)$, simulate datasets, and plot the \divt{} values
against the summary statistics calculated from the resulting datasets
(Figure~\ref{figSaturationPlot}).
Clearly, the priors used by \citet{Oaks2012} with upper limits on \divt{} of five
and 10 suffered from little to no effect from saturation.
Even at divergence times of 20 coalescent units, there is still signal in the
summary statistics used by \msb (Figure~\ref{figSaturationPlot}).
Thus, the assertion of \citet{Hickerson2013} does not apply to at least
two of the priors used by \citet{Oaks2012} and, as a result, does not
explain the bias they found.
